HMM Model development

### 2020-05-15 dev/hmm_model_devel.Rmd
Preparing gen. quants for posterior predictive stuff

```{r}
noisy_states_in_sbc <- FALSE
sbc_generator <- function() {
  data <- hmm_simulator(50, 20, 3, use_noisy_states = noisy_states_in_sbc)
  standata <- make_standata_hmm(data$observed$formula, 
                                serie_data = data$observed$serie_data, 
                                rate_data = data$observed$rate_data, 
                                hidden_state_data = data$observed$hidden_state_data, 
                                initial_states = data$observed$initial_states,
                                observed_state_data = data$observed$observed_state_data,
                                sensitivity_low_bound = data$observed$sensitivity_low_bound)

@@

sbc_res <- sbc(model_single, generator = sbc_generator, N_steps = 200, control = list(adapt_delta = adapt_delta))

@@

```{r}
library(brms)
```

```{r}
```

@@

test_data <- data.frame(a = c(1,2,3), b = c(0.5,1.0,1.5), x1 = c("A"), x2 = c(0,1,2))
f <- a ~ 0 + (0 + x2 | a | x1)
# make_stancode(f, data = test_data)
#brms::make_standata(f, data = test_data)
xx <- brms::brmsformula(f)

xx$resp

stan_llh.rate_hmm <- function( ... ) {
  ""
}

.family_rate_hmm <- function() {

}

ff <-

make_stancode(a ~ 0 + x2, family = ff, data = test_data)

>>>>

```{r}
noisy_states_in_sbc <- TRUE
sbc_generator <- function() {
  data <- hmm_simulator(20, 15, 2, use_noisy_states = noisy_states_in_sbc)
  standata <- make_standata_hmm(data$observed$formula, 
                                serie_data = data$observed$serie_data, 
                                rate_data = data$observed$rate_data, 
                                hidden_state_data = data$observed$hidden_state_data, 
                                initial_states = data$observed$initial_states,
                                observed_state_data = data$observed$observed_state_data,
                                sensitivity_low_bound = data$observed$sensitivity_low_bound)

@@

sbc_res <- sbc(model_single, generator = sbc_generator, N_steps = 50, control = list(adapt_delta = adapt_delta))

@@

## Apply to Grein et al. dataset

@@

  breathing_data_orig <- readxl::read_excel(here::here("public_data", "Grein_et_al.xlsx"), na = c("")) %>%
    select(-Remdesivir_Last_Day) %>%
    pivot_longer(starts_with("Day_"), names_prefix = "Day_", names_to = "day", values_to = "breathing") %>%
    filter(!is.na(breathing)) %>%
    transmute(
      patient = Patient,
      breathing = if_else(breathing %in% c("LoO2", "HiO2"), "Oxygen", breathing),
      day = as.integer(day)) %>%
    group_by(patient) %>%
    mutate(breathing = if_else(breathing == "ND", breathing[which.max(day[breathing %in% c("AA", "Oxygen", "NIPPV", "MV", "ECMO")])], breathing)) %>%
    ungroup() %>%
    mutate(
      breathing = factor(breathing, levels = c("Discharge", "AA", "Oxygen", "NIPPV", "MV", "ECMO", "Death"), ordered = TRUE)
    )
